Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-04 Paper/main.tex
Phil's modifications to text

\subsection{Objectives}
\fxnote{fix order of objectives} In the current study on stable marine
boundary layers, we aim to build on the previous work in the
literature and complete several objectives.  First, we examine the
domain and mesh requirements necessary to capture the turbulent scales
for the stable offshore boundary layers.  Secondly, two LES solvers
within the ExaWind project will be compared in this study: the
unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
used to calculate the same SBL, and the relative differences between
the codes are reported.  Finally, a series of stable boundary layer
conditions will be computed using AMR-Wind which match the
measurements of Archer et al. \cite{archer2016predominance}.  The
behavior of the stable boundary layers, including mean flow quantities
and turbulent statistics, are examined and compared to the neutral and
unstable cases computed in \cite{cheung2020large}.

>>>>

\subsection{Objectives}
In the current study on stable marine
boundary layers, we aim to build on the previous work in the
literature and complete several objectives.  First, we examine the
domain and mesh requirements necessary to capture the turbulent scales
for the stable offshore boundary layers.  Secondly, two LES solvers
within the ExaWind project will be compared in this study: the
unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
used to calculate the same SBL, and the relative differences between
the codes are reported.  Finally, a series of stable boundary layer
conditions will be computed using AMR-Wind which match the
measurements of Archer et al. \cite{archer2016predominance}.  The
behavior of the stable boundary layers, including mean flow quantities
and turbulent statistics, are examined and compared to the neutral and
unstable cases computed in \cite{cheung2020large}.

### 2020-12-04 Paper/results.tex
Phil's modifications to text

Additional information about the mesh and domain requirements can be
drawn by examining the turbulent integral length scale $L$.  This
lengthscale can be calculated from $\langle R_{11}(\boldsymbol{\xi})
\rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.

Based on this longitudinal length scale, we also determined the
overall domain size necessary for stable ABL calculations.  To provide
sufficient space to ensure development and decorrelation of turbulent
structures, domain sizes of approximately 10 times the longitudinal
lengthscale is recommended.  However, the inclusion of sample probes
with sufficient separation distance to accurately calculate $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
requirements.  Assuming the longitudinal length scales on the order of
30 m, we estimated a minimum domain size of 750 m $\times$ 750 m in the
horizontal directions for both the Nalu-Wind and AMR-Wind LES
calculations.

@@

\subsection{Comparison of stable offshore ABL for different wind speeds and stabilities}

Using the results of the stable cases described in \ref{sec:CFDsetup},
as well as the neutral and unstable ABL computations from the previous study in
Cheung et al. \cite{cheung2020large}, we can examine the influence of wind speed and
stratification on offshore ABL behavior.  In this section we first
compare the differences between the three stable ABL cases, and then
compare their behavior with the previously computed neutral and
unstable counterparts.

\subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
\fxnote{Explain why AMR-Wind only}
From AMR-Wind calculations of the stable ABL at 5 m/s, 10 m/s, and
15 m/s, a number of quantities can be computed to compare with the
measured targets from Archer et al \cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal lengthscale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20 m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.

@@

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5 m/s, 10 m/s,
    and 15 m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5 m/s, 10 m/s, and
    15 m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Additional information about the mesh and domain requirements can be
drawn by examining the turbulent integral length scale $L$.  This
lengthscale can be calculated from $\langle R_{11}(\boldsymbol{\xi})
\rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{11}(\xi) \rangle \: {\textrm d}\xi
\end{equation}
and the results are shown in table \ref{tab:GridStudyLscale}.  With a
resolution of 2.5m, the ratio of the longitudinal length scale to the
grid size $L/\textrm{d}x \approx 10.1$, while in the lateral direction
$L/\textrm{d}x \approx 2.36$, suggesting even finer resolution is
required to capture the lateral scales.  This may be a critical
consideration when resolving both the lateral and longitudinal
turbulent scales are important, such as in SBL simulations with
turbine interactions.  However, in other situations, the additional
computational cost incurred may be prohibitive and only the
longitudinal component can be resolved.

Based on the longitudinal length scale, we also determined the
overall domain size necessary for stable ABL calculations.  To provide
sufficient space to ensure development and decorrelation of turbulent
structures, domain sizes of approximately 10 times the longitudinal
lengthscale is recommended.  However, the inclusion of sample probes
with sufficient separation distance to accurately calculate $\langle
R_{11}(\boldsymbol{\xi}) \rangle$ roughly doubles the domain size
requirements.  Assuming the longitudinal length scales on the order of
30 m, we estimated a minimum domain size of 750 m $\times$ 750 m in the
horizontal directions for both the Nalu-Wind and AMR-Wind LES
calculations.

@@

\subsection{Comparison of the stable offshore ABL for different wind speeds and stabilities}

Using the results of the stable cases described in \ref{sec:CFDsetup},
as well as the neutral and unstable ABL computations from the previous
study in Cheung et al. \cite{cheung2020large}, we can examine the
influence of wind speed and stratification on offshore ABL behavior.
In this section, we use the AMR-Wind code to calculate the stable ABL
at 5 m/s, 10 m/s, and 15 m/s because of its computational efficiency
and comparable accuracy to Nalu-Wind.  From the results we first
compare the differences between the three stable ABL cases, and then
compare their behavior with the previously computed neutral and
unstable counterparts.

\subsubsection{\label{sec:stableABLStats} ABL integrated quantities}

From AMR-Wind LES calculations, a number of quantities can be computed
to compare with the measured targets from Archer et al
\cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal lengthscale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20 m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.

@@

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5 m/s, 10
    m/s, and 15 m/s boundary layers. The dashed horizontal line
    corresponds to the measurement height z=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5 m/s, 10 m/s,
    and 15 m/s boundary layers. The dashed horizontal line corresponds
    to the measurement height z=20 m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
